### 2024-02-09 Conclusion.tex
Synced 1-layer chapter with revised manuscript and mostly updated Chapter 5

\subsection{Improvement in HSI parameter extraction}
Chapter \ref{chap:HSImodel} demonstrates the importance of noise reduction in HSI data collection intra-operatively in order to obtain precise parameter extraction. For this reason, the snapshot hyperspectral imaging system presented in Chapters \ref{chap:SWB} and \ref{chap:HSImodel} should be improved to reduce noise in the acquired hypercubes. To aid the fitting process, the optimal central wavelengths of the bands should be identified alongside the optimal number of bands whilst retaining low acquisition times. Finally, Chapter \ref{chap:1layer} demonstrates the rapid decline in parameter extraction quality with small imperfections in the absorbance and scattering models input. For this reason, the validation of the optical absorbance and scattering models used for biological tissue is likely a key avenue of future study to improve parameter extraction quality using these methods. This could include use of inverse Monte Carlo, inverse Adding Doubling, or deep learning methods to calculate ground truth absorption and scattering coefficients of healthy brain tissues. Whilst this work has begun, it has not been compared to current optical modelling with standard parameter values to determine the accuracy of these\cite{Sabino2016, Eggert1987, Shapey2022, Hokr2021}. There could also be further research into the chromophores included in these models; this could include measurement of a wider range of chromophores (such as lipids which do not have prominent measurements from human samples), potential interactions between biological components which could affect the spectra similarly to that seen in Chapter \ref{chap:1layer}, and the measurement of biological chromophores in media that more closely replicates that of biological tissue as this can impact the extinction coefficients as seen in Chapter \ref{chap:1layer}.

>>>>

\subsection{Improvement in HSI parameter extraction}
Chapter \ref{chap:HSImodel} demonstrates the importance of noise reduction in HSI data collection in order to obtain precise parameter extraction. For this reason, the snapshot hyperspectral imaging system and data processing presented in Chapters \ref{chap:SWB} and \ref{chap:HSImodel} should be improved to reduce noise in the acquired hypercubes. To aid the fitting process, the optimal central wavelengths of the bands should be identified alongside the optimal number of bands whilst retaining low acquisition times. Testing of the models investigated with intra-operative snapshot hyperspectral data should also be carried out to understand the quality of parameter extraction with this imaging system.

Finally, Chapter \ref{chap:1layer} demonstrates the rapid decline in parameter extraction quality with small imperfections in the absorbance and scattering models input. For this reason, the validation of the optical absorbance and scattering models used for biological tissue is likely a key avenue of future study to improve parameter extraction quality using these methods. This could include use of inverse Monte Carlo, inverse Adding Doubling, or deep learning methods to calculate ground truth absorption and scattering coefficients of healthy brain tissues. Whilst this work has begun, it has not been compared to current optical modelling with standard parameter values to determine the accuracy of these\cite{Sabino2016, Eggert1987, Shapey2022, Hokr2021}. There could also be further research into the chromophores included in these models; this could include measurement of a wider range of chromophores (such as lipids which do not have prominent measurements from human samples), potential interactions between biological components which could affect the spectra similarly to that seen in Chapter \ref{chap:1layer}, and the measurement of biological chromophores in media that more closely replicates that of biological tissue as this can impact the extinction coefficients as seen in Chapter \ref{chap:1layer}.

### 2024-02-09 Introduction.tex
Synced 1-layer chapter with revised manuscript and mostly updated Chapter 5

% This work aims to use a Hyperspectral Imaging (HSI) camera to extract semantic and physiologically relevant data in real-time during neuro-oncological surgery. These data are expected to aid decision-making, thereby reducing cognitive workload for the surgeons without compromising patient outcomes. The following introduction summarises the fundamentals of brain tumours and current operating practice.  This is followed by a summary of Hyperspectral Imaging, key data post-processing steps, and an outline of the thesis.

\section{Hyperspectral imaging}
Hyperspectral imaging (HSI) measures diffuse reflectance spectra using multiple channels, which are narrow spectral measurements centred around a given wavelength. In comparison, traditional imaging only collects three broad channels to create a conventional RGB (red, green, blue) image. This provides higher spectral resolution than traditional imaging whilst maintaining a wide field of view. This technique can also
be referred to as multispectral imaging when there is a low number of bands, however for simplicity we will refer to this as HSI in all cases~\cite{Clancy2020}.

@@

HSI is widely used in many applications and has shown promise for medical imaging~\cite{Lu2014,Giannoni2018,Calin2014,Shapey2019}. It is hoped that the increased spectral resolution would allow computation of clinically relevant physiological parameters, such as chromophore concentration. These parameters are hypothesised to aid decision making intra-operatively, where neurosurgery provides a good candidate for this due to it's precise nature as discussed in the following sections.

@@

This demonstrates the need to improve real-time, spatially-resolved, visualisation of tumour boundaries and vascularisation particularly for low-grade tumours where fluorescence imaging has limited application due to the low accumulation of fluorophore in these less aggressive tumours~\cite{Belykh2023, Kiesel2021}.

>>>>

% This work aims to use a Hyperspectral Imaging (HSI) camera to extract semantic and physiologically relevant data in real-time during neuro-oncological surgery. These data are expected to aid decision-making, thereby reducing cognitive workload for the surgeons without compromising patient outcomes. The following introduction summarises the fundamentals of brain tumours and current operating practice.  This is followed by a summary of Hyperspectral Imaging, key data post-processing steps, and an outline of the thesis.
%
\section{Tissue parameter extraction technologies}

\subsection{Optical Coherance Tomography}
Optical Coherance Tomography (OCT) is a non-contact 3D imaging modality which provides both spatial and depth information of the tissue imaged. The technique utilises a reference beam and a sample beam, where using Fourier transforms to analyse the interference of the backscattered light from the sample beam with the reference beam returns the depth of scattering structures at the spatial location measured~\cite{Fercher2003}. By scanning the beam across the sample tissue, a 3D image can be constructed~\cite{Fercher2003}. Traditionally OCT utilises near-infrared wavelengths (NIR) due to the deeper penetration into biologically tissue, however recent advances have shown that using visible wavelengths allows oxygen saturation of vessels to be computed~\cite{Shu2017}. Whilst this provides spatially resolved oxygenation information of major vessels, significant attenuation is required for this calculation limiting its application to tissue directly~\cite{Shu2017}.

\subsection{Raman spectroscopy}
Raman spectroscopy is a technique that observes wavelength shifts of laser light due to inelastic scattering. These shifts correspond to vibrational modes of the scattering molecules which enables the chemical composition of the sample to be identified~\cite{Kong2015}. This technique has been used to identify tumour margins primarily in brain and breast cancer surgeries and has recently overcome many of the challenges to its adoption including acquisition speed and accuracy~\cite{Kong2015}. There have also been advances in the use of this technique for oxygen saturation measurement, however this is limited to measurement of the oxygen saturation in vessels and requires calibration with blood samples of known oxygen saturation which is highly complex and disruptive to surgical workflow~\cite{TorresFilho2016}.

\subsection{Probe-based diffuse reflectance spectroscopy}
Diffuse reflectance spectroscopy measures diffusely scattered light from a sample in order to gain information on the absorbance and scattering properties of this sample. Whilst this work focuses on Hyperspectral imaging as a method of diffuse reflectance spectroscopy, there are many fibre-optic probe-based systems for these measurements. These systems provide highly accurate diffuse reflectance spectra in a point-based measurement, however they do not provide wide-field imaging~\cite{Nishidate2015}. This limitation, however, can be overcome by stitching together measurements from multiple probe locations~\cite{Thrapp2020}. Whilst this technique is non-contact is requires very close probe-sample distances for high quality data measurement~\cite{Nishidate2015}.

\subsection{Hyperspectral imaging}
Hyperspectral imaging (HSI) measures diffuse reflectance spectra using multiple channels, which are narrow spectral measurements centred around a given wavelength. In comparison, traditional imaging only collects three broad channels to create a conventional RGB (red, green, blue) image. HSI provides higher spectral resolution than traditional imaging whilst maintaining a wide field of view. This technique can also be referred to as multispectral imaging when there is a low number of bands, however for simplicity we will refer to this as HSI in all cases~\cite{Clancy2020}.

HSI is widely used in many applications and has shown promise for medical imaging~\cite{Lu2014,Giannoni2018,Calin2014,Shapey2019}. The ability to measure diffuse reflectance spectra with spatial resolution allows much more information to be displayed in a single acquisition than probe-based alternatives. This allows both spatial and spectral information to be interpretated, computationally or visually, simultaneously which may provide further insights~\cite{Seidlitz2022}. Similarly, the increased spectral resolution may allow for computation of clinically relevant physiological parameters, such as chromophore concentrations, which cannot be determined from traditional RGB imaging so reducing subjectivity~\cite{Seidlitz2022}, and enables computation for tissues directly in addition to examining vasculature. Additionally, HSI is a non-invasive, non-contact imaging modality which can be used in a compact format with minimal disruption to workflow~\cite{Thoenissen2023, Ebner2021, MacCormac2023}. We also address complexities in calibration as Chapter \ref{chap:SWB}. Despite the increased data storage and computational requirements for the large quantities of data associated with HSI~\cite{Altamimi2022}, these advantages suggest that HSI could be a useful tool to elucidate physiological parameters intra-operatively.

@@

Spatial Frequency Domain Imaging (SFDI) can be utilised with HSI to provide accurate, spatially-resolved, sampling depth information by projecting patterns of different frequencies which are either spatially or temporally demodulated~\cite{Gioux2019}. Whilst this provides useful added information, for example for accurate white balancing, this method is highly disruptive to surgical workflow and so is not utilised in this work.

Throughout this thesis a snapshot HSI camera with a 4x4 mosaic pattern across the sensor (Ximea utilising the IMEC CMV2K-SSM4X4-VIS sensor, Germany) is chosen which enables fast data acquisition and integration into a variety of imaging configurations. This sensor is combined with an f=35mm coupler (Karl Storz, NDTec, VCam HD-F-35 - Camera Lens Adapter, Germany) and an exoscope (Karl Storz Endoscopy, VITOM Telescope 0° w Integ. Illuminator, UK) for imaging. This creates a standalone imaging system which is combined with various light sources. In this work, this system is used in a highly controlled manner either mounted to a seven degree of freedom robot (LBR, KUKA med7 R800, Germany) to enable multiple images to be taken with a constant reproducible camera position relative to the subject, or mounted to an optical breadboard to ensure fixed camera position, both of which can be seen in Figure \ref{fig:HSIsetups}. This system, however, is also being adapted for clinical use with the use of sterile drapes and a handheld configuration, detailed in Chapter \ref{chap:SWB}~\cite{Budd2023}. 
\begin{figure}[h]
    \centering 
    \begin{subfigure}[ht!]{0.27\textwidth}
	\includegraphics[width=\textwidth]{KUKAHSI}
	\caption{}
	\label{fig:KUKAHSI}
    \end{subfigure}
    \begin{subfigure}[ht!]{0.17\textwidth}
        \includegraphics[width=\textwidth]{imagephantoms}
        \caption{}
        \label{fig:ScopeHSI}
    \end{subfigure}
    \caption{Snapshot HSI system comprising the sensor (Ximea utilising the IMEC CMV2K-SSM4X4-VIS sensor, Germany), an f=35mm coupler (Karl Storz, NDTec, VCam HD-F-35 - Camera Lens Adapter, Germany), and an exoscope (Karl Storz Endoscopy, VITOM Telescope 0° w Integ. Illuminator, UK) mounted to a seven degree of freedom robot (LBR, KUKA med7 R800, Germany) (\ref{fig:KUKAHSI}) or a static optical breadboard (\ref{fig:ScopeHSI}).}
    \label{fig:HSIsetups}
\end{figure}
%
%It is hoped that the increased spectral resolution would allow computation of clinically relevant physiological parameters, such as chromophore concentration. These 
It is hypothesised that spatially resolved, clinically relevant, physiological parameters extracted using HSI could aid decision making intra-operatively. Neurosurgery provides a good candidate for this due to it's precise nature. 
%as discussed in the following sections.

@@

This demonstrates the need to improve real-time, spatially-resolved, visualisation of tumour boundaries and vascularisation particularly for low-grade tumours where fluorescence imaging has limited application due to the low accumulation of fluorophore in these less aggressive tumours~\cite{Belykh2023, Kiesel2021, Jaber2019}.
